% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\newif\ifbibliography
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% remove section numbering
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{section title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{subsection title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}

\usetheme[]{Rochester}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={When Big Business Loses (?) : The Political Economy of Regulation in the Context of Noisy Politics},
  pdfauthor={Oscar Dumas; Hyung Won Kim; Nikolaos Vichos},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}


\title{When Big Business Loses (?) : The Political Economy of Regulation
in the Context of Noisy Politics}
\author{Oscar Dumas \and Hyung Won Kim \and Nikolaos Vichos}
\date{}

\begin{document}
\frame{\titlepage}


\begin{frame}[fragile]{Overview of Presentation}
\phantomsection\label{overview-of-presentation}
\begin{enumerate}
\tightlist
\item
  Introduction
\item
  Theoretical Framework and Important Concepts: Noisy Politics
\item
  Side-By-Side: Paper Summaries and Critical Discussion
\item
  Synthesis: What Unites the Two Papers?
\item
  Contextualization: Noisy Politics and the Political Economy of
  Regulation
\item
  Conclusion and Discussion
\end{enumerate}
\end{frame}

\section{Introduction}\label{introduction}

\begin{frame}{Texts}
\phantomsection\label{texts}
\begin{itemize}
\tightlist
\item
  Massoc, Elsa. 2019. ``Taxing Stock Transfers in the First Golden Age
  of Financial Capitalism: Political Salience and the Limits on the
  Power of Finance.'' \emph{Socio-Economic Review} 17 (3): 503--22.
  https://doi.org/10.1093/ser/mwx039.
\item
  Feldmann, Magnus, and Glenn Morgan. 2021. ``Brexit and British
  Business Elites: Business Power and Noisy Politics.'' \emph{Politics
  \& Society} 49 (1): 107--31. https://doi.org/10.1177/0032329220985692.
\end{itemize}
\end{frame}

\begin{frame}{Research Focus}
\phantomsection\label{research-focus}
\begin{block}{Massoc (2019) :}
\phantomsection\label{massoc2019}
\begin{itemize}
\tightlist
\item
  Why did powerful financial actors fail to prevent the adoption of
  stock-transfer taxes in France and New York?
\item
  \textbf{Focus}: how public discontent + political framing raised
  salience and undermined ``quiet politics.''
\end{itemize}
\end{block}

\begin{block}{Feldmann and Morgan (2021):}
\phantomsection\label{feldmann2021}
\begin{itemize}
\tightlist
\item
  Under what conditions can business elites be effective in a context of
  noisy politics, and why did their influence differ between 1975 and
  2016?
\item
  \textbf{Focus}: how incentives, legitimacy, and cohesion shape
  business influence in high-politicization referendum campaigns.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{What brings these papers together?}
\phantomsection\label{what-brings-these-papers-together}
Both papers examine how political visibility and public contestation
reshape business/financial influence

\begin{itemize}
\item
  Massoc (2019) shows how politicization of a tax issue enabled
  politicians to override strong financial lobbying.
\item
  Feldmann and Morgan (2021) analyze how changing political conditions
  over time affect business effectiveness in high-visibility referendum
  campaigns.\\
\end{itemize}

\begin{block}{\textbf{Common Question}}
\phantomsection\label{common-question}
\begin{itemize}
\tightlist
\item
  \emph{Under what conditions do business actors struggle to assert
  influence?}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}[allowframebreaks]{Bibliography}
\phantomsection\label{bibliography}
\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-feldmann2021}
Feldmann, Magnus, and Glenn Morgan. 2021. {``Brexit and British Business
Elites: Business Power and Noisy Politics*.''} \emph{Politics \&
Society} 49 (1): 107--31.
\url{https://doi.org/10.1177/0032329220985692}.

\bibitem[\citeproctext]{ref-massoc2019}
Massoc, Elsa. 2019. {``Taxing Stock Transfers in the First Golden Age of
Financial Capitalism: Political Salience and the Limits on the Power of
Finance.''} \emph{Socio-Economic Review} 17 (3): 503--22.
\url{https://doi.org/10.1093/ser/mwx039}.

\end{CSLReferences}
\end{frame}




\end{document}
